%!TEX program = xelatex
\documentclass[11pt,a4paper]{article}
\usepackage{mies}

% Metadata
\hypersetup{
    pdfauthor = {Dr. Emmett Brown, Marty McFly, Doc Manhattan},
    pdftitle = {The Economics of Time Travel: A Theoretical Exploration},
}

\title{The Economics of Time Travel: A Theoretical Exploration}
\author{
    Dr. Emmett Brown\thanks{Institute of Temporal Studies},~
    Marty McFly\thanks{Hill Valley University},~
    Doc Manhattan\thanks{Quantum Economics Lab}
}
\date{December 2049\\[3em]
\textbf{}
}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
\noindent This paper explores the impact of time travel on economic theories. We discuss how market dynamics, labor productivity, and the concept of scarcity are affected when the temporal dimension is altered. Our analysis reveals unique challenges and paradoxes that arise in a world where time travel is possible, reshaping the fundamental principles of economics.
\end{abstract}

\vspace{3em}

\noindent
\textbf{Keywords:} Time Travel, Economic Paradoxes, Temporal Markets, Quantum Finance

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
"Roads? Where we're going, we don't need roads." - This article embarks on a theoretical journey, exploring the intersection of time travel and economics. We delve into how disrupting the time continuum could redefine the core concepts of economic theory.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Time-Money Paradox}
In this section, we examine the peculiar dynamics of the time value of money in a world where time is a variable resource.

\section{Supply and Demand Across Eras}
Here, we humorously analyze the impact of time travelers on historical market supply and demand.

\section{Temporal Arbitrage Opportunities}
This section explores the concept of using time travel for economic gain, such as investing in stocks with the knowledge of the future.

\section{Labor Markets and Work Hours}
We discuss the potential effects of time travel on labor markets, work hours, and overall productivity in a whimsical manner.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TIKZ FIGURE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{TikZ Figure Example}
Below is an example of a TikZ figure illustrating a hypothetical time travel market model.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\draw (0,0) -- (4,0) node[right] {Time};
\draw (0,0) -- (0,4) node[above] {Economic Impact};
\draw (0.5,0.5) .. controls (2,2) and (3,3) .. (3.5,3.5);
\draw[dashed] (0.5,0.5) -- (3.5,3.5);
\node at (2,1) {Hypothetical Curve};
\end{tikzpicture}
\caption{Time Travel Economic Impact Over Time}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Example Table}
The following table shows fictional data on time travel frequency and economic indicators.

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|}
\hline
Year & Time Travel Events & Economic Impact (in Billions) \\
\hline
2023 & 5 & \$100 \\
2024 & 8 & \$150 \\
2025 & 12 & \$200 \\
\hline
\end{tabular}
\caption{Time Travel Frequency and Economic Impact}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CONCLUSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
We conclude with a lighthearted summary of the paradoxes and impracticalities introduced by incorporating time travel into economic models.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\section{Robustness Checks}
Our robustness checks include absurd, pseudo-scientific tests to validate the economics of time travel, such as measuring inflation rates during the Jurassic era.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{aer}
\bibliography{bibliography}

\end{document}
